Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignment with the stellar disk

### 2019-07-18 Document/paper.tex
edit

@@

The caveat of the studies mentioned above is that they do not
follow baryons in the whole cosmological context. 
Other studies overcome this limitation by using resimulations 
\citep{Abadi_et_al._2010,Bryan_et_al._2013} finding that the
feeback related to star formation in the disk drives the strenght of
the round effect. 
Recently \cite{2018arXiv180907255C} made a study in a cosmological
simulation to compare the effect of including baryons. They do find,
on average, rounder halo shapes once hydrodynamic effects are
included, but it is uncertain the strenght of this statistical effect
on galaxies similar to the MW.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_angles_triaxiality_MHD.pdf}
\end{center}
\caption{Changse of angle alignment of the dark
  matter halo and stellar disk at two different radii ($R_{200}/16$
  and $0.25R_{200}$) as a function of the baryonic disk properties
  already explored in Figure \ref{fig:disk_correlations}.  
  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
  considerable missalignments occurr.
 at different radii
 and baryonic disk properties. 
 The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
\label{fig:alignment_correlations}
\end{figure*}

>>>>

\citep{Dubinski91}

@@

Rounding effect of baryons
\citep{Dubinski94}

The caveat of the studies mentioned above is that they do not
follow baryons in the whole cosmological context. 
Other studies overcome this limitation by using resimulations 
\citep{Abadi_et_al._2010,Bryan_et_al._2013} finding that the
feeback related to star formation in the disk drives the strenght of
the round effect.

Abadi2010 -> well aligned countours.

Recently \cite{2018arXiv180907255C} made a study in a cosmological
simulation to compare the effect of including baryons. They do find,
on average, rounder halo shapes once hydrodynamic effects are
included, but it is uncertain the strenght of this statistical effect
on galaxies similar to the MW.

\citep{JingSuto02} report the twisting in their simulations.
They also find a universal radius where the alignment of the internal 
region (defined as the region with 2500 times the critical density) 
is perfect with the shell under consideration.
They blame it on high c/b and undecided vectors.
but in our case c/b increases monotonically with radius, and the
alignment with the disk is not monotonous. In our case this cannot be
the only explanation as the triaxiliaty correlation with the twist 
strongly depends on the radius.

\citep{Pedrosa10}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
\end{center}
\caption{Changse of angle alignment of the dark
  matter halo and stellar disk at two different radii ($R_{200}/16$
  and $0.25R_{200}$) as a function of the baryonic disk properties
  already explored in Figure \ref{fig:disk_correlations}.  
  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
  considerable missalignments occurr.
 at different radii
 and baryonic disk properties. 
 The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
\label{fig:alignment_correlations}
\end{figure*}
